---
title: "select_for_garden"
author: "Bria Long"
date: "2023-10-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(Hmisc)
library(magick)
```

# Read in previous files
```{r}
multiafc_exp = read_csv('exp1_all_trials2023-04-11.csv') 
```

## Eliminate items we didn't use
```{r}
multiafc_exp_actual <- multiafc_exp %>%
  filter(!Word1 %in% c('scrabble','honey')) 
  # filter(trial_type %in% c('hard','easy','distal')) # no practice in this script
```

## Eliminate items from IRT model (2pl model on mutliafc data)
```{R}
items_to_elim <- read_csv('suggested_removed_items.csv') 
```

## Filter these
```{r}
exp2_clip_items <- multiafc_exp_actual %>%
  filter(!Word1 %in% items_to_elim$item)
```

## Read in csv with target/distractors we're using on PPVT
Download csvs, need to do some wrangling here

```{R}
age5 <- read_csv(here::here('stimuli/manual_curation/item_csvs/age5.csv'))  %>%
  filter(!is.na(`Uploaded to drive?`)) %>%
  filter(`Image found` =='y') %>%
  select(Target, Distractor) %>%
  rename(Word1 = Target, Word2 = Distractor) %>%
  mutate(Word1 = capitalize(Word1), Word2 = capitalize(Word2))  %>%
  mutate(Folder = Word1)  %>%
  mutate(item_num = '_1')


age6 <- read_csv(here::here('stimuli/manual_curation/item_csvs/age6.csv'))  %>%
  filter(!is.na(`Uploaded to Drive`)) %>%
  filter(`image found` == 'y') %>%
  select(Taget, Distractor) %>%
  rename(Word1 = Taget, Word2 = Distractor) %>%
  mutate(Word1 = capitalize(Word1), Word2 = capitalize(Word2))  %>%
  mutate(Folder = paste0(Word1,'/','Squared')) %>%
  mutate(item_num = '')


age7 <- read_csv(here::here('stimuli/manual_curation/item_csvs/age7.csv'))  %>%
  filter(`Image found` == 'y') %>%
  select(Target, Distractor)  %>%
  rename(Word1 = Target, Word2 = Distractor) %>%
  mutate(Word1 = capitalize(Word1), Word2 = capitalize(Word2))  %>%
  mutate(Folder = Word1)  %>%
  mutate(item_num = '')
```

# Get all manual items

```{r}


culled_items <- c('Elbow','Feather','Dancing','Shoulder','Target','Buckle', 'Floating')
# don't have mald audio for feather
# elbow/shoulder too much skin
# target no images
# dancing wasn't a great image
# buckle not enough images
# floating was a weird target image, too sexual
```

```{r}
clip_overlap <- unique(exp2_clip_items$Word1)
clip_dist_overlap <- unique(exp2_clip_items$Word2)
clip_items_all <- c(clip_overlap, clip_dist_overlap)
# 
# # no target words overlap
# overlap <- all_manual %>%
#   filter(str_to_lower(Word1) %in% clip_overlap)
# 
# # some targte words in manual are distractors for clip
# overlap <- all_manual %>%
#   filter(str_to_lower(Word1) %in% clip_dist_overlap)
```

# filter overlaps between sets
```{R}
all_manual <- age5 %>%
  full_join(age6)  %>%
  full_join(age7)  %>%
  group_by(Word1) %>%
  filter(!Word1 %in% culled_items) %>%
  filter(Word1 != Word2)   %>%
  filter(!str_to_lower(Word1) %in% clip_items_all) %>%
  filter(!str_to_lower(Word2) %in% clip_items_all)
  
```


Look in the MALD database and filter to items that have recording (most of them)
```{r}
load(here::here('stimuli/existing_datasets/MALD/mald_metadata/MALD1_1_ItemData.rda'))

mald_items <- capitalize(items$Item)
```

Filter and creat path to audio file
```{r}
all_manual <- all_manual %>%
  filter(Word1 %in% mald_items) %>%
  mutate(Audio_File_Word_1 = paste0(here::here('stimuli/existing_datasets/MALD/MALD1_rw/'), Word1, '.wav')) 
  
```



# Write out images and audio into new folders
Here are our new paths
```{r}
today = Sys.Date()
image_out_dir = paste0("stimuli/selected_stimuli/exp3_garden/images_final",today,'/')
audio_out_dir = paste0("stimuli/selected_stimuli/exp3_garden/audio_final",today,'/')

dir.create(here::here(image_out_dir))
dir.create(here::here(audio_out_dir))
```

Create paths to old and new copies of the images and aduio files
```{r}


all_trials <- all_manual %>%
  mutate(Word_1_path_jpg=here::here(paste0('stimuli/manual_curation/items/',Folder,'/', Word1,item_num,'.jpg')))  %>%
  mutate(Word_1_path=here::here(paste0('stimuli/manual_curation/items/',Folder,'/', Word1, item_num,'.png')))  %>%
  mutate(Word_2_path=here::here(paste0('stimuli/manual_curation/items/',Folder,'/', Word2, item_num,'.png')))  %>%
  mutate(Word_2_path_jpg=here::here(paste0('stimuli/manual_curation/items/',Folder,'/', Word2, item_num,'.jpg')))  %>%
  mutate(Word_1_new_path = here::here(paste0(image_out_dir, str_to_lower(Word1),'.jpg'))) %>%
  mutate(Word_2_new_path = here::here(paste0(image_out_dir,str_to_lower(Word2),'.jpg')))  %>%
  mutate(audio_new_path = here::here(paste0(audio_out_dir,str_to_upper(Word1),'.wav')))   

```

These are the trials where we can find the png and it's square and that we want
```{r}
trials_ok_png <- all_trials %>%
  filter(file.exists(Word_1_path)) %>%
  filter(file.exists(Word_2_path)) 

```

These are distractors I manually eliminated.
```{r}
missing <- all_trials %>%
  filter(!file.exists(Word_2_path))  # these 
```

These should all be empty

```{r}
need_jpg <- all_trials %>%
  filter(file.exists(Word_1_path_jpg)) %>%
  filter(file.exists(Word_2_path_jpg))
```

```{R}
cant_find <- all_trials %>%
  filter(!file.exists(Word_1_path))  %>%
  filter(!file.exists(Word_1_path_jpg))
```

```{r}
num_dist <- trials_ok_png %>%
  group_by(Word1) %>%
  dplyr::summarize(dist = length(unique(Word2))) %>%
  filter(dist <3)

to_check <- trials_ok_png %>%
  filter(Word1 %in% num_dist$Word1)

```

# Did a bunch of manual rejiggering of items/distractors to ensure no duplicates
```{r}
# manual_items  = c(all_manual$Word1, all_manual$Word2)
```

```{r}
# this_word = 'sundial'
# all_manual %>% filter(Word2 == 'Watch')
# # 
# this_word %in% str_to_lower(manual_items)
# this_word %in% clip_items_all
```

# Load, resize, and copy these images/audio to a new folder

## For png files
```{r}

for (trial in seq.int(1,length(trials_ok_png$Word1))) {
  print(trial)
  
  img = magick::image_scale(image_read(trials_ok_png$Word_1_path[trial]), "300x300")
  image_write(img, path = trials_ok_png$Word_1_new_path[trial], quality=80)
  
  img2 = magick::image_scale(image_read(trials_ok_png$Word_2_path[trial]), "300x300")
  image_write(img2, path = trials_ok_png$Word_2_new_path[trial], quality=80)
  
  fs::file_copy(trials_ok_png$Audio_File_Word_1[trial], trials_ok_png$audio_new_path[trial], overwrite=TRUE)
  
}
```




## Now recopy all the clip items and audio
```{r}
exp2_clip_items_clean <- exp2_clip_items %>%
  select(Word1, Word2, trial_type) %>%
  mutate(Audio_File_Word_1 = paste0(here::here('stimuli/existing_datasets/MALD/MALD1_rw/'), Word1, '.wav')) %>%
  mutate(Word_1_path=here::here(paste0('stimuli/selected_stimuli/exp2_multiafc/exp1_images_2023-04-11/',Word1, '.jpg')))  %>%
  mutate(Word_2_path=here::here(paste0('stimuli/selected_stimuli/exp2_multiafc/exp1_images_2023-04-11/',Word2, '.jpg')))  %>%
  mutate(Word_1_new_path = here::here(paste0(image_out_dir, str_to_lower(Word1),'.jpg'))) %>%
  mutate(Word_2_new_path = here::here(paste0(image_out_dir,str_to_lower(Word2),'.jpg')))  %>%
  mutate(audio_new_path = here::here(paste0(audio_out_dir,str_to_upper(Word1),'.wav')))  

```


```{r}
for (trial in seq.int(1,length(exp2_clip_items_clean$Word1))) {
  print(trial)
  img = magick::image_scale(image_read(exp2_clip_items_clean$Word_1_path[trial]), "300x300")
  image_write(img, path = exp2_clip_items_clean$Word_1_new_path[trial])
  
  img2 = magick::image_scale(image_read(exp2_clip_items_clean$Word_2_path[trial]), "300x300")
  image_write(img2, path = exp2_clip_items_clean$Word_2_new_path[trial])
  
  fs::file_copy(exp2_clip_items_clean$Audio_File_Word_1[trial], exp2_clip_items_clean$audio_new_path[trial], overwrite=TRUE)
  
  fs::file_copy(exp2_clip_items_clean$Audio_File_Word_1[trial], exp2_clip_items_clean$audio_new_path[trial], overwrite=TRUE)
}
```




# Merge together clip and manual datasets into a single csv
```{r}
manual_items <- trials_ok_png %>%
  select(Word1, Word2) %>%
  mutate(wordPairing = 'hard', source = 'manual', itemGroup = 'test') %>%
  group_by(Word1) %>%
  mutate(distractorId = row_number())  
   
```
```{r}
all_trials_garden <- exp2_clip_items_clean %>%
  mutate(wordPairing = trial_type) %>%
  select(Word1, Word2, wordPairing) %>%
  mutate(source = 'clip', itemGroup = 'test') %>%
  mutate(distractorId = case_when(wordPairing == 'hard' ~ 1, 
                                  wordPairing == 'easy' ~ 2, 
                                  wordPairing == 'distal' ~ 3)) %>%
  full_join(manual_items)
  
```
should be empty
```{R}
check <- all_trials_garden %>%
  group_by(Word1) %>%
  dplyr::summarize(num_dist = length(unique(Word2))) %>%
  filter(num_dist != 3)
  
```


```{r}
check <- all_trials_garden %>%
  mutate(Word1_filename = paste0(here::here(image_out_dir), capitalize(Word1),'.png')) %>%
  mutate(Word2_filename = paste0(here::here(image_out_dir), capitalize(Word2),'.png')) %>%
  filter(file.exists(Word1_filename))  %>%
  filter(file.exists(Word2_filename)) 
```

```{R}
item_summary <- all_trials_garden %>%
  group_by(source, wordPairing) %>%
  dplyr::summarize(num_items = length(unique(Word1)))
  
```

Check that this worked
```{r}
image_files <- list.files(path = here::here(image_out_dir), pattern = ".png", ignore.case = TRUE)
print(image_files)


any_missing <- all_trials_garden %>%
  mutate(image_name = paste0(capitalize(Word1),'.png')) %>%
  filter(!image_name %in% image_files)

any_missing_dist <- all_trials_garden %>%
  mutate(image_name = paste0(capitalize(Word2),'.png')) %>%
  filter(image_name %in% image_files)

uh_what <- all_trials_garden %>%
  ungroup() %>%
  filter(Word2 %in% unique(all_trials_garden$Word1))
```


# Save out CSV file
```{r}
all_trials_garden <- all_trials_garden %>%
  mutate(Word1 = str_to_lower(Word1)) %>%
  mutate(Word2 = str_to_lower(Word2))  %>%
  mutate(itemGroup = case_when(
              !wordPairing %in% c('hard','easy','distal') ~ "practice_or_catch", 
               wordPairing %in% c('hard','easy','distal') ~ "test" ))


write_csv(all_trials_garden, file=paste0(here::here('stimuli/selected_stimuli/exp3_garden/'),'all_trials_garden_final', today(), '.csv'))
```
