---
title: "Wrangle_datasets"
author: "Bria Long"
date: "2024-05-08"
output: html_document
---


# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, cache=FALSE)
```

```{r}
library(tidyverse)
library(lubridate)
library(ggthemes)
library(assertthat)
library(langcog) # for CIs
library(mirt)
library(ggpubr)
library(knitr)
library(dplyr)
library(here)
library(lme4)
library(lmerTest)
library(digest)
library(viridis)
```


## Load data from multiafc task
First load all metadata we'll need for the items
```{r}
test_corpus <- read_csv(here::here("data/item_metadata/new_test.csv")) %>%
  filter(!Word1 %in% c('honey','scrabble')) # manually excluded
```

# New merged data post preprcoessing
```{r}
multiafc_combined <- read_csv(here::here("data/raw/multiAFC_4AFC_clean_combined_data_20240909.csv"))
```

# Load metadata
## examine items across aoa bins
```{r}
clip_cor_by_model <- read_csv(here::here("data/item_metadata/exp1_all_trials2023-04-11.csv")) %>%
  select(Word1, Word2, trial_type, cor, AoA_Est_Word2, AoA_Est_Word1) %>%
  rename(wordPairing = trial_type) %>%
  rename(clip_cor = cor) %>%
  filter(Word1 %in% unique(test_corpus$Word1))  %>%
  filter(!Word1 %in% c('honey','scrabble')) %>% # manually excluded for symmetry across blocks
  ungroup() %>%
  mutate(AoA_Bin = ntile(AoA_Est_Word1,3)) %>%
  mutate(AoA_Bin_Name = factor(AoA_Bin,  levels = c('1','2','3'), labels = c("Early AoA", "Med AoA", "Late AOA"))) 
```

```{r}
sanity <- clip_cor_by_model %>%
  group_by(AoA_Bin_Name) %>%
  summarize(num_words = length(unique(Word1)), meanAoA = mean(AoA_Est_Word1))
```


# Load data
Load data and restrict to clip words (no dutch)
```{r}
test_clip_cor <- read_csv(here::here("data/item_metadata/exp1_all_trials2023-04-11.csv")) %>%
  select(Word1, Word2, trial_type, cor, AoA_Est_Word2, AoA_Est_Word1) %>%
  rename(wordPairing = trial_type) %>%
  rename(clip_cor = cor) %>%
  filter(Word1 %in% unique(test_corpus$Word1)) %>%
  filter(!Word1 %in% c('honey','scrabble')) # manually excluded for symmetry across blocks
```

Create data structure and merge that has clip cor==1 for target selection
```{r}
test_clip_cor_identity <- test_clip_cor %>%
  select(Word1, AoA_Est_Word1) %>%
  distinct(Word1, AoA_Est_Word1) %>%
  mutate(Word2 = Word1) %>%
  mutate(AoA_Est_Word2 = AoA_Est_Word1) %>%
  mutate(clip_cor = 1) %>%
  mutate(wordPairing = 'target')

test_clip_cor <- test_clip_cor %>%
  full_join(test_clip_cor_identity) %>%
  arrange(Word1)

```

Rename meta data structures so that they merge correctly with trial data
```{R}
clip_to_join <- test_clip_cor %>%
  rename(targetWord = Word1) %>%
  rename(answerWord = Word2)
```

```{r}
test_corpus <- test_corpus %>%
  left_join(test_clip_cor)

sum(is.na(test_corpus$clip_cor))
```

## Read in bing & garden data
```{r}
bing = read_csv(here::here('data/raw/all_bing_data_for_item_info.csv'))  %>%
  mutate(age_group = as.numeric(floor(age_in_months/12))) %>%
  select(-block)
```


```{r}
garden = read_csv(here::here('data/raw/all_garden_roar_data_with_age.csv'))   %>%
  mutate(start_time = as.character(start_time)) %>%
  filter(assessment_stage=='test_response')  %>%
  select(-assessment_stage) %>%
  mutate(age_group = floor(age_in_years))  %>%
  select(pid, targetWord, answerWord, correct, rt, numAFC, age_in_years, age_group) 

```

## Read in multi-afc adult data
Set age to "25" so we can plot it together
```{r}
adults <- read_csv(here::here("data/raw/multi-afc-april28.csv"))  %>%
  mutate(age_group = as.numeric(25)) %>% # set 
  filter(task == 'test_response') %>%
  select(pid, targetWord, answerWord, correct, rt, numAFC, age_group) 
```



## Make trial-levels data structure across all ages
```{R}
trial_data <- multiafc_combined %>%
  mutate(age_group = floor(ageMonths/12)) %>%
  filter(age_group<15) %>%
  filter(group!='B') %>%
  full_join(garden) %>% # manually merge garden instead for age/pid difficulties
  full_join(adults)  %>%
  filter(targetWord %in% clip_to_join$targetWord) %>% 
  left_join(clip_to_join) 
  
```



## Parse out item-level responses 
Join together and clean datastructures
```{r}
df.multiAFC.trials <- trial_data %>% 
  left_join(test_corpus %>% rename(targetWord = "Word1", answerWord = "Word2")) %>%
  filter(is.na(itemGroup) | (itemGroup == "test")) %>% 
  mutate(wordPairing = ifelse(is.na(wordPairing), "target", wordPairing)) %>%
  filter(!targetWord %in%  c("ant","ball","bear","scrabble","honey")) %>% 
  select(pid, answerWord, targetWord, numAFC, correct, rt, wordPairing, age_group, clip_cor) 

df.4AFC.trials <- df.multiAFC.trials %>% 
  filter(numAFC==4)

rm(df.multiAFC.trials) # force 4afc from now on
```

# Now get rid of weird participants
# Get rid of people who are at chance
```{r}
at_chance <- df.4AFC.trials %>%
  group_by(age_group, pid) %>%
  summarize(pc = mean(correct), num_trials = length(unique(targetWord)))  %>%
  filter(age_group>6) %>%
  filter(pc<.3)
```

```{r}
df.4AFC.trials.clean <- df.4AFC.trials %>%
  filter(!pid %in% at_chance$pid)
```


Create age/group and number of participants for filtering for plots / age-based analyses
```{r}
age_group_pid <- df.4AFC.trials.clean %>%
  group_by(age_group) %>%
  summarize(num_pids = length(unique(pid))) 
```

We have `r sum(age_group_pid$num_pids)-205` children aged 3-11 years, and 205 adults.





## Create intermediate data structures
Now write code to fill out response pattern for all possible target/distractor responses on each age for each age...for use later.

```{r}
full_item_structure_4AFC <- clip_to_join %>%
  mutate(numAFC = 4)
```

Now fill this out by all ages in the dataset, oof this was annoying
```{r}
full_item_structure_by_age_4afc = map_df(age_group_pid$age_group, ~full_item_structure_4AFC %>% mutate(age_group = .x)) 
```


## Calculate proportion of times participants chose an image
First do this across all age groups -- for basic item plots.
```{r}
df.4AFC.totalAttempts <- df.4AFC.trials.clean %>% 
  group_by(targetWord, numAFC) %>% 
  tally() %>% 
  dplyr::rename(totalAttempts = n)

# this includes target word selection
df.4AFC.distractor.summary <- df.4AFC.trials.clean %>% 
  group_by(targetWord,  answerWord, wordPairing) %>% 
  tally() %>%
  left_join(df.4AFC.totalAttempts) %>% 
  mutate(perc = n/totalAttempts) %>%
  full_join(full_item_structure_4AFC) %>% # need to fill out item structure (but not by age)
  mutate(perc = replace_na(perc, replace=0))
```

Look at histogram of how often an item was attempted overal
```{r}
hist(df.4AFC.totalAttempts$totalAttempts)
```

Look at histograms of how often the target was chosen
```{r}
target_pc <- df.4AFC.distractor.summary %>%
  filter(wordPairing=='target') %>%
  arrange(perc)

# hist(target_pc$perc)
```



# Construct response dataframe now by age group 
```{r}
df.4AFC.totalAttempts.byAge <- df.4AFC.trials.clean %>% 
  group_by(targetWord, age_group) %>% 
  tally() %>% 
  dplyr::rename(totalAttempts = n)

df.4AFC.distractor.summary.byAge <- df.4AFC.trials.clean %>% 
  group_by(targetWord,  answerWord, wordPairing, age_group) %>%
  summarise(n = n(), medianRT = median(rt)) %>% 
  left_join(df.4AFC.totalAttempts.byAge) %>% 
  mutate(perc = n/totalAttempts) %>%
  full_join(full_item_structure_by_age_4afc)

```

```{r}
what <- df.4AFC.distractor.summary.byAge %>%
  filter(is.na(perc))
```


There are some missing observations because these items were never even SEEN  -- these are true NAs and mostly concentrated in the youngest kids

```{r}
unseen_target_items_by_age_group <- df.4AFC.totalAttempts.byAge %>%
  full_join(full_item_structure_by_age_4afc %>% distinct(targetWord, age_group)) %>%
  filter(is.na(totalAttempts))
```

couple of sanity checks for missing values that shuold be zero
```{r}
assert_that(sum(is.na(df.4AFC.distractor.summary.byAge$age_group))==0)
assert_that(sum(is.na(df.4AFC.distractor.summary.byAge$clip_cor))==0)
  
```



There are some missing observations because these items were never chosen on a given trial/age group -- need to fill those out

But we also have some target/distractor/age group pairings that are VERY sparsely populated -- that makes sense especially as kids get more accurate and don't choose distal items. We also have relatively few younger kids.

```{r}
hist(df.4AFC.distractor.summary.byAge$totalAttempts)
```

## These are true NAs because never seen
```{r}
unseen_items <- df.4AFC.distractor.summary.byAge  %>%
  right_join(unseen_target_items_by_age_group)
```


But we n ow need to populate "0" value in the percent chosen category for distractor items that were never chosen and so not in the data structure 


OK, put it back all together
```{r}
df.4AFC.distractor.summary.byAge.clean <- df.4AFC.distractor.summary.byAge %>%
  anti_join(unseen_items) %>% # get rid of unseen items
  mutate(perc = replace_na(perc, replace=0)) %>% # now replace non-chosen with 0
  full_join(unseen_items) %>% # rejoin these  true NAs
  ungroup() %>%
  mutate(AoA_Bin = ntile(AoA_Est_Word1,3)) %>%
  mutate(AoA_Bin_Name = factor(AoA_Bin,  levels = c('1','2','3'), labels = c("Early AoA", "Med AoA", "Late AOA"))) 
```

Make sure we have it all filled out correctly
```{r}
sanity_check <- df.4AFC.distractor.summary.byAge.clean %>%
  filter(numAFC==4) %>%
  group_by(age_group, targetWord) %>%
  summarize(count = n()) 

assert_that(sum(sanity_check$count!=4)==0) # 
```


```{r}
save(df.4AFC.distractor.summary.byAge.clean, file=here::here('data/preprocessed/summary_by_distractor.Rdata'))

save(df.4AFC.trials.clean, file=here::here('data/preprocessed/all_trial_data.Rdata'))
```



